---
title: "Week 5 Visualization Activity"
author: "Jai Chi Cham"
date: "2022-09-17"
output: word_document
---


```{r setup, include=FALSE}
#code chunk to call the installed packages
library(dplyr)
library(ggplot2)
```


##Histogram for variable avg_hatecrimes_per_100k_fbi
"avg_hatecrimes_per_100k_fbi" displays the average annual hate crimes per 100,000 population as per FBI data. Timeframe is year 2010-2015. The histogram displays that the highest frequency of average annual hate crimes is range from 0-2 hate crimes per 100,000 population.The highest frequency is 25. Only one state has an average hate crime range from 10-12 per 100,000 population. 


```{r, echo = FALSE, warning=FALSE}
hate_crimes <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/hate-crimes/hate_crimes.csv")
avg_hatecrimes_per_100k_fbi = hate_crimes$avg_hatecrimes_per_100k_fbi
hist(avg_hatecrimes_per_100k_fbi, col="darkmagenta")
```


##Scatter plot displaying relationship between share_voters_vited_trump and avg_hatecrimes_per_100k_fbi
The below scatter plot displaying relationship between average annual hate crimes per 100,000 population and the share_voters_vited_trump. The plot shows that states with higher share_voter_voted_Trump have higher average annual hate crimes per 100,000 population. 

```{r, echo = FALSE, warning=FALSE}
hate_crimes <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/hate-crimes/hate_crimes.csv")
ggplot(hate_crimes, aes(x=share_voters_voted_trump, y=avg_hatecrimes_per_100k_fbi)) +  
  geom_point(colour = "blue") +   ylim(1, 5)
```

